Carbon stocks in aboveground biomass for Colombian mangroves with associated uncertainties

### 2018-01-06 LaTeX_source_files/Article/Article_mangroves.tex
Edited figure captions

%\begin{figure}
%\includegraphics[%scale=0.4
%width=\textwidth
%]{Figures/Cdensity_and_TotalCstock.pdf} 
%\caption{
Figure 1. Aboveground biomass (AGB) density (Mg C ha$^{-1}$) and total carbon stock in AGB for Colombian mangroves (Tg C). 
%}
%\label{fig:Csotck}
%\end{figure}

@@

%\begin{figure} 
%\includegraphics[%scale=0.4
%width=\textwidth
%]{Figures/AGBsamplingEffort.pdf} 
%\caption{
Figure 2. Number of necessary sampling units of AGB density required to reduce current uncertainties at 10\% and 5\% level for Caribbean, Pacific and total Colombian mangroves.%} \label{fig:samplingEffort}
%\end{figure}

@@

%\begin{figure} 
%\includegraphics[%scale=0.4
%width=\textwidth
%]{Figures/Globalmodelsvs.pdf} 
%\caption{
Fiigure 3. Observed vs. predicted AGB density (Mg ha$^{-1}$). Predicted values: using global models \citep{Twilley1992, CONL:CONL12060} and observed data: current data available for mangrove areas in Colombia}% \label{fig:globalModels}
%\end{figure}

@@

%\begin{figure} 
%\includegraphics[%scale=0.4
%width=\textwidth
%]{Figures/AGBdensity_map_final.pdf} 
%\caption{
Figure 4. Map of predicted AGB density (Mg ha$^{-1}$) based on the candidate models classified as ``substantial weight models''%} %\label{fig:Predicted AGB density map}
%\end{figure}

@@

\bibliography{Bibliography/Bibliography_Article_Mangroves}
%\bibliographystyle{apalike}

>>>>

@@

@@

@@

@@

%\bibliography{../Bibliography/Bibliography_Article_Mangroves}
%\bibliographystyle{apalike}

\begin{thebibliography}{51}
\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
\expandafter\ifx\csname url\endcsname\relax
  \def\url#1{\texttt{#1}}\fi
\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi

\bibitem[{Adame et~al.(2013)Adame, Kauffman, Medina, Gamboa, Torres, Caamal,
  Reza, and Herrera-Silveira}]{Adame2013}
Adame, M.~F., Kauffman, J.~B., Medina, I., Gamboa, J.~N., Torres, O., Caamal,
  J.~P., Reza, M., Herrera-Silveira, J.~a., Jan. 2013. {Carbon Stocks of
  Tropical Coastal Wetlands within the Karstic Landscape of the Mexican
  Caribbean.} PloS one 8~(2), e56569.
\newline\urlprefix\url{http://www.pubmedcentral.nih.gov/articlerender.fcgi?artid=3572964\&tool=pmcentrez\&rendertype=abstract}

\bibitem[{Alongi(2011)}]{Alongi2011}
Alongi, D.~M., Jun. 2011. {Carbon payments for mangrove conservation: ecosystem
  constraints and uncertainties of sequestration potential}. Environmental
  Science \& Policy 14~(4), 462--470.
\newline\urlprefix\url{http://linkinghub.elsevier.com/retrieve/pii/S1462901111000177}

\bibitem[{Alongi(2014)}]{Alongi2014}
Alongi, D.~M., 2014. {Carbon cycling and storage in mangrove forests.} Annual
  review of marine science 6, 195--219.
\newline\urlprefix\url{http://www.ncbi.nlm.nih.gov/pubmed/24405426}

\bibitem[{Anaya et~al.(2009)Anaya, Chuvieco, and Palacios-Orueta}]{Anaya2009}
Anaya, J.~a., Chuvieco, E., Palacios-Orueta, A., 2009. {Aboveground biomass
  assessment in Colombia: A remote sensing approach}. Forest Ecology and
  Management 257~(4), 1237--1246.

\bibitem[{Arag\~{a}o et~al.(2009)Arag\~{a}o, Malhi, Metcalfe, Silva-Espejo,
  Jim\'{e}nez, Navarrete, Almeida, Costa, Salinas, Phillips, Anderson, Baker,
  Goncalvez, Huam\'{a}n-Ovalle, Mamani-Sol\'{o}rzano, Meir, Monteagudo,
  Pe\~{n}uela, Prieto, Quesada, Rozas-D\'{a}vila, Rudas, {Silva Junior}, and
  V\'{a}squez}]{Aragao2009}
Arag\~{a}o, L. E. O.~C., Malhi, Y., Metcalfe, D.~B., Silva-Espejo, J.~E.,
  Jim\'{e}nez, E., Navarrete, D., Almeida, S., Costa, a. C.~L., Salinas, N.,
  Phillips, O.~L., Anderson, L. O.~., Baker, T.~R., Goncalvez, P.~H.,
  Huam\'{a}n-Ovalle, J., Mamani-Sol\'{o}rzano, M., Meir, P., Monteagudo, A.,
  Pe\~{n}uela, M.~C., Prieto, A., Quesada, C.~a., Rozas-D\'{a}vila, A., Rudas,
  A., {Silva Junior}, J.~a., V\'{a}squez, R., 2009. {Above- and below-ground
  net primary productivity across ten Amazonian forests on contrasting soils}.
  Biogeosciences Discussions 6~(1), 2441--2488.

\bibitem[{Bates et~al.(2015)Bates, Maechler, Bolker, and Walker}]{Bates:2015aa}
Bates, D., Maechler, M., Bolker, B.~M., Walker, S., 2015. Fitting linear
  mixed-effects models using {lme4}. ArXiv e-print; in press, \emph{Journal of
  Statistical Software}.
\newline\urlprefix\url{http://arxiv.org/abs/1406.5823}

\bibitem[{Blanco et~al.(2012)Blanco, Estrada, Ortiz, and Urrego}]{Blanco2012}
Blanco, J.~F., Estrada, E.~a., Ortiz, L.~F., Urrego, L.~E., 2012.
  {Ecosystem-Wide Impacts of Deforestation in Mangroves: The Urab\'{a} Gulf
  (Colombian Caribbean) Case Study}. ISRN Ecology 2012, 1--14.

\bibitem[{Boucher et~al.(2014)Boucher, Garcia-Huidobro, Herr, Laffoley, and
  Podvin}]{Boucher2014}
Boucher, J., Garcia-Huidobro, T., Herr, D., Laffoley, D., Podvin, K., 2014.
  {Panama and Colombia Blue Carbon Preparedness Report of the Panama City
  workshop , March 2014 Advanced draft Panama and Colombia Blue Carbon
  Preparedness - the Action Plan}. Tech. rep., IUCN.

\bibitem[{Chave et~al.(2005)Chave, Andalo, Brown, Cairns, Chambers, Eamus,
  F\"{o}lster, Fromard, Higuchi, Kira, Lescure, Nelson, Ogawa, Puig, Ri\'{e}ra,
  and Yamakura}]{Chave2005}
Chave, J., Andalo, C., Brown, S., Cairns, M.~a., Chambers, J.~Q., Eamus, D.,
  F\"{o}lster, H., Fromard, F., Higuchi, N., Kira, T., Lescure, J.-P., Nelson,
  B.~W., Ogawa, H., Puig, H., Ri\'{e}ra, B., Yamakura, T., Aug. 2005. {Tree
  allometry and improved estimation of carbon stocks and balance in tropical
  forests.} Oecologia 145~(1), 87--99.
\newline\urlprefix\url{http://www.ncbi.nlm.nih.gov/pubmed/15971085}

\bibitem[{Clark et~al.(2001)Clark, Brown, Kicklighter, Chambers, Thomlinson,
  Ni, and Holland}]{Clark2001}
Clark, D.~a., Brown, S., Kicklighter, D.~W., Chambers, J.~Q., Thomlinson,
  J.~R., Ni, J., Holland, E.~a., 2001. {Net primary production in tropical
  forests: An evaluation and synthesis of existing field data}. Ecological
  Applications 11~(2), 371--384.
\newline\urlprefix\url{http://www.esajournals.org/doi/abs/10.1890/1051-0761(2001)011\%5B0371:NPPITF\%5D2.0.CO\%3B2}

\bibitem[{Cohen et~al.(2013)Cohen, Kaino, Okello, Bosire, Kairo, Huxham, and
  Mencuccini}]{Cohen2013968}
Cohen, R., Kaino, J., Okello, J., Bosire, J., Kairo, J., Huxham, M.,
  Mencuccini, M., 2013. Propagating uncertainty to estimates of above-ground
  biomass for kenyan mangroves: A scaling procedure from tree to landscape
  level. Forest Ecology and Management 310, 968 -- 982.
\newline\urlprefix\url{http://www.sciencedirect.com/science/article/pii/S0378112713006610}

\bibitem[{{De la Pe\~{n}a} et~al.(2010){De la Pe\~{n}a}, Rojas, and {De la
  Pe\~{n}a}}]{DelaPena2010}
{De la Pe\~{n}a}, A., Rojas, C.~A., {De la Pe\~{n}a}, M., 2010. {Valoraci\'{o}n
  econ\'{o}mica del manglar por el almacenamiento de carbono ,}. Cl\'{\i}o
  America 4~(7), 133--150.

\bibitem[{Didan et~al.(2015)Didan, Huete, and SIPS-NASA}]{MODIS2015}
Didan, K., Huete, A., SIPS-NASA, M., 2015. {MOD13Q1 MODIS and the Terra
  Vegetation Indices 16-Day L3 Global 250m SIN Grid V006. NASA EOSDIS LP DAAC}.
\newline\urlprefix\url{http://doi.org/10.5067/MODIS/MOD13Q1.006}

\bibitem[{Donato et~al.(2011)Donato, Kauffman, Murdiyarso, Kurnianto, Stidham,
  and Kanninen}]{Donato2011}
Donato, D.~C., Kauffman, J.~B., Murdiyarso, D., Kurnianto, S., Stidham, M.,
  Kanninen, M., 05 2011. Mangroves among the most carbon-rich forests in the
  tropics. Nature Geosci 4~(5), 293--297.
\newline\urlprefix\url{http://dx.doi.org/10.1038/ngeo1123}

\bibitem[{Ewel et~al.(1998)Ewel, Twilley, and Ong}]{Ewel1998}
Ewel, K., Twilley, R., Ong, J., 1998. Different kinds of mangrove forests
  provide different goods and services. Global Ecology \& Biogeography Letters
  7~(1), 83--94.
\newline\urlprefix\url{http://dx.doi.org/10.1111/j.1466-8238.1998.00275.x}

\bibitem[{{FAO}(2007)}]{FAO2007}
{FAO}, 2007. {The world´s mangroves 1980-2005. A thematic study prepared in
  the framework of the Global Forest Resources Assessment 2005}. FAO, Food and
  Agriculture Organization of the United Nations.
\newline\urlprefix\url{http://www.fao.org/docrep/010/a1427e/a1427e00.htm}

\bibitem[{Fearnside and Laurance(2004)}]{Fearnside2004}
Fearnside, P.~M., Laurance, W.~F., 2004. {Tropical deforestation and
  greenhouse-gas emissions}. Ecological Applications 14~(4), 982--986.

\bibitem[{Giri et~al.(2011{\natexlab{a}})Giri, Ochieng, Tieszen, Zhu, Singh,
  Loveland, Masek, and Duke}]{Giri2011dataset}
Giri, C., Ochieng, E., Tieszen, L., Zhu, Z., Singh, A., Loveland, T., Masek,
  J., Duke, N., 2011{\natexlab{a}}. Global mangrove forests distribution, 2000.
\newline\urlprefix\url{http://dx.doi.org/10.7927/H4J67DW8}

\bibitem[{Giri et~al.(2011{\natexlab{b}})Giri, Ochieng, Tieszen, Zhu, Singh,
  Loveland, Masek, and Duke}]{Giri2011}
Giri, C., Ochieng, E., Tieszen, L.~L., Zhu, Z., Singh, A., Loveland, T., Masek,
  J., Duke, N., 2011{\natexlab{b}}. {Status and distribution of mangrove
  forests of the world using earth observation satellite data}. Global Ecology
  and Biogeography 20, 154--159.
\newline\urlprefix\url{http://doi.wiley.com/10.1111/j.1466-8238.2010.00584.x}

\bibitem[{Guti{\'e}rrez-V{\'e}lez and DeFries(2013)}]{Gutierrez2013}
Guti{\'e}rrez-V{\'e}lez, V.~H., DeFries, R., 2013. Annual multi-resolution
  detection of land cover conversion to oil palm in the {Peruvian Amazon}.
  Remote Sensing of Environment 129, 154 -- 167.
\newline\urlprefix\url{http://www.sciencedirect.com/science/article/pii/S003442571200421X}

\bibitem[{Herr et~al.(2012)Herr, Pidgeon, and Laffoley}]{Herr2012}
Herr, D., Pidgeon, E., Laffoley, D., 2012. {Blue Carbon Policy Framework 2.0:
  Based on the discussion of the International Blue Carbon Policy Working
  Group}. IUCN; CI, Gland, Switzerland and Arlington, USA.

\bibitem[{Herz(1999)}]{Herz1999}
Herz, R., 1999. {Procesamiento digital de im{\'a}genes de sat{\'e}lite para el
  reconocimiento de patrones en los manglares}. In: Y{\'a}nez-Arancibia, A.,
  Dom{\'\i}nguez-Lara, L.~A. (Eds.), Ecosistemas de Manglar en Am{\'e}rica
  Tropical. Instituto de Ecolog\'{i}a A.C. Mexico, Ch.~8, pp. 83--108.

\bibitem[{Hijmans et~al.(2005)Hijmans, Cameron, Parra, Jones, and
  Jarvis}]{Hijmans2005}
Hijmans, R.~J., Cameron, S.~E., Parra, J.~L., Jones, P.~G., Jarvis, A., 2005.
  {Very high resolution interpolated climate surfaces for global land areas}.
  International Journal of Climatology 25~(15), 1965--1978.

\bibitem[{Huete et~al.(2002)Huete, Didan, Miura, Rodriguez, Gao, and
  Ferreira}]{Huete2002}
Huete, A., Didan, K., Miura, T., Rodriguez, E., Gao, X., Ferreira, L., 2002.
  Overview of the radiometric and biophysical performance of the modis
  vegetation indices. Remote Sensing of Environment 83~(1), 195 -- 213.
\newline\urlprefix\url{http://www.sciencedirect.com/science/article/pii/S0034425702000962}

\bibitem[{Hutchison et~al.(2014)Hutchison, Manica, Swetnam, Balmford, and
  Spalding}]{CONL:CONL12060}
Hutchison, J., Manica, A., Swetnam, R., Balmford, A., Spalding, M., 2014.
  Predicting global patterns in mangrove forest biomass. Conservation Letters
  7~(3), 233--240.
\newline\urlprefix\url{http://dx.doi.org/10.1111/conl.12060}

\bibitem[{IDEAM(2015)}]{IDEAM2015}
IDEAM, July 2015. Entidades ambientales ponen en marcha primera fase de
  inventario forestal nacional.
\newline\urlprefix\url{http://www.ideam.gov.co/web/sala-de-prensa/noticias/-/asset_publisher/96oXgZAhHrhJ/content/entidades-ambientales-ponen-en-marcha-primera-fase-de-inventario-forestal-nacional}

\bibitem[{INVEMAR(2007)}]{INVEMAR2007}
INVEMAR, 2007. {Informe del Estado de los Recursos Marinos y Costeros en
  Colombia: A\~{n}o 2006}. Tech. rep., Instituto de investigaciones Marinas y
  Costeras "Jos\'{e} Benito Vives de Andr\'{e}is".

\bibitem[{INVEMAR(2014)}]{INVEMAR2014}
INVEMAR, 2014. {Informe del Estado de los Recursos Marinos y Costero en
  Colombia A\~{n}o 2013}. Tech. rep., Instituto de Investigaciones Marinas y
  Costeras "Jos\'{e} Benito Vives de Andr\'{e}is" - INVEMAR, Santa Marta.

\bibitem[{IPCC(2003)}]{IPCC2003}
IPCC, 2003. {Intergovernmental Panel on Climate Change Good Practice Guidance
  for Land Use , Land-Use Change and Forestry}. IGES, Japan.
\newline\urlprefix\url{the Institute for Global Environmental Strategies (IGES)
  for the IPCC ?}

\bibitem[{IPCC(2006)}]{IPCC2006}
IPCC, 2006. {2006 IPCC Guidelines for National Greenhouse Gas Inventories}.
  Vol. 4: Agriculture, Forestry and Other Land Use. IGES.
\newline\urlprefix\url{http://www.ipcc-nggip.iges.or.jp/public/2006gl/pdf/4\_Volume4/V4\_04\_Ch4\_Forest\_Land.pdf}

\bibitem[{Jardine and Siikam{\"a}ki(2014)}]{1748-9326-9-10-104013}
Jardine, S.~L., Siikam{\"a}ki, J.~V., 2014. A global predictive model of carbon
  in mangrove soils. Environmental Research Letters 9~(10), 104013.
\newline\urlprefix\url{http://stacks.iop.org/1748-9326/9/i=10/a=104013}

\bibitem[{Kauffman and Donato(2012)}]{Kauffman2012}
Kauffman, J.~B., Donato, D.~C., 2012. {Protocols for the measurement,
  monitoring and reporting of structure, biomass and carbon stocks in mangrove
  forests}. Working Paper~86, CIFOR, Bogor, Indonesia.

\bibitem[{Komiyama et~al.(2008)Komiyama, Ong, and Poungparn}]{Komiyama2008128}
Komiyama, A., Ong, J.~E., Poungparn, S., 2008. Allometry, biomass, and
  productivity of mangrove forests: A review. Aquatic Botany 89~(2), 128 --
  137, mangrove Ecology -- Applications in Forestry and Costal Zone Management.
\newline\urlprefix\url{http://www.sciencedirect.com/science/article/pii/S0304377007001829}

\bibitem[{Kristensen et~al.(2008)Kristensen, Bouillon, Dittmar, and
  Marchand}]{Kristensen2008}
Kristensen, E., Bouillon, S., Dittmar, T., Marchand, C., 2008. Organic carbon
  dynamics in mangrove ecosystems: A review. Aquatic Botany 89~(2), 201 -- 219,
  mangrove Ecology -- Applications in Forestry and Costal Zone Management.
\newline\urlprefix\url{http://www.sciencedirect.com/science/article/pii/S0304377007001817}

\bibitem[{Lema and Polan\'{\i}a(2007)}]{Lema2007}
Lema, L.~F., Polan\'{\i}a, J., 2007. {Estructura y din\'{a}mica del manglar del
  delta del r\'{\i}o Rancher\'{\i}a , Caribe colombiano}. Revista de
  Biolog\'{\i}a Tropical 55~(1), 11--21.

\bibitem[{{L{\'{o}}pez Rodr{\'{i}}guez} et~al.(2013){L{\'{o}}pez
  Rodr{\'{i}}guez}, Sierra-Correa, and Lozano-Rivera}]{LopezRodriguez2013}
{L{\'{o}}pez Rodr{\'{i}}guez}, {\'{A}}., Sierra-Correa, P.~C., Lozano-Rivera,
  P., 2013. {Criteria for Incorporating the Guidelines of the Integrated
  Coastal Zone Management (ICZM) in Territorial Land Use Planning: Study Case
  for the Colombian Pacific Coastal Area}. International Journal of Marine
  Science International Journal of Marine Science International Journal of
  Marine Science 33303~(292929), 225--237.
\newline\urlprefix\url{http://ijms.sophiapublisher.com}

\bibitem[{MacDicken(1997)}]{MacDicken1997}
MacDicken, K.~G., 1997. {A guide to monitoring carbon storage in forestry and
  agroforestry projects}. Winrock International Institute for Agricultural
  Development.

\bibitem[{Maniatis and Mollicone(2010)}]{Maniatis2010}
Maniatis, D., Mollicone, D., 2010. {Options for sampling and stratification for
  national forest inventories to implement REDD+ under the UNFCCC.} Carbon
  balance and management 5~(December), 9.
\newline\urlprefix\url{http://www.cbmjournal.com/content/5/1/9}

\bibitem[{Mazerolle(2015)}]{Mazerolle:2015aa}
Mazerolle, M.~J., 2015. AICcmodavg: Model selection and multimodel inference
  based on (Q)AIC(c). R package version 2.0-3.
\newline\urlprefix\url{http://CRAN.R-project.org/package=AICcmodavg}

\bibitem[{{Monsalve, A., Ram\'irez, G.}(2015)}]{Malaga2015}
{Monsalve, A., Ram\'irez, G.}, 2015. Caracterizaci{\'o}n de la estructura y
  contenido de carbono de diez parcelas permanentes establecidas en el {\'a}rea
  de jurisdicci{\'o}n del consejo comunitario la plata, bah{\'\i}a m{\'a}laga,
  valle del cauca. Tech. rep., INVEMAR-Carbono\&Bosques.

\bibitem[{Murray et~al.(2012)Murray, Watt, Cooley, and Pendleton}]{Murray2012}
Murray, B.~C., Watt, C.~E., Cooley, D.~M., Pendleton, L.~H., 2012. {Coastal
  Blue Carbon and the United Nations Current Status and Future Directions}.
  Tech. Rep. NI PB 12-01, Duke Nicholas Institute for Environmental Policy
  Solutions.
\newline\urlprefix\url{www.nicholasinstitute.duke.edu}

\bibitem[{Nellemann et~al.(2009)Nellemann, Corcoran, Duarte, Vald{\'e}s, {De
  Young}, Fonseca, and Grimsditch}]{Nellemann2009}
Nellemann, C., Corcoran, E., Duarte, C.~M., Vald{\'e}s, L., {De Young}, C.,
  Fonseca, L., Grimsditch, G., 2009. {Blue carbon: A Rapid Response
  Assessment.} United Nations Environment Programme, GRID-Arendal,
  www.grida.no.
\newline\urlprefix\url{http://www.grida.no/files/publications/blue-carbon/BlueCarbon\_screen.pdf}

\bibitem[{Phillips et~al.(2011)Phillips, Duque, Yepes, Cabrera, Navarrete,
  Davila, and Cardenas}]{Phillips2011}
Phillips, J.~F., Duque, A., Yepes, A., Cabrera, K., Navarrete, D.~A., Davila,
  E., Cardenas, D., 2011. {Estimacion de las reservas actuales (2010) de
  carbono almacenadas en la biomasa aerea en bosques naturales de Colombia}.
  Ministerio de Ambiente, Vivienda y Desarrollo Territorial, IDEAM, Bogot.

\bibitem[{Polan\'{\i}a et~al.(2015)Polan\'{\i}a, , Urrego, and
  Agudelo}]{Polania2015}
Polan\'{\i}a, J., , Urrego, L.~E., Agudelo, C.~M., 2015. {Recent advances in
  understanding Colombian mangroves}. Acta Oecologica 63, 82--90.

\bibitem[{Saenger and Snedaker(1993)}]{Saenger1993}
Saenger, P., Snedaker, S.~C., 1993. {Pantropical trends in mangrove
  above-ground biomass and annual litterfall}. Oecologia 96~(3), 293--299.

\bibitem[{Sierra et~al.(2007)Sierra, del Valle, Orrego, Moreno, Harmon, Zapata,
  Colorado, Herrera, Lara, Restrepo, Berrouet, Loaiza, and
  Benjumea}]{Sierra2007}
Sierra, C.~A., del Valle, J.~I., Orrego, S.~A., Moreno, F.~H., Harmon, M.~E.,
  Zapata, M., Colorado, G.~J., Herrera, M.~A., Lara, W., Restrepo, D.~E.,
  Berrouet, L.~M., Loaiza, L.~M., Benjumea, J.~F., 2007. Total carbon stocks in
  a tropical forest landscape of the porce region, colombia. Forest Ecology and
  Management 243~(2-3), 299--309.

\bibitem[{Spalding et~al.(2010)Spalding, Kainuma, and Collins}]{Spalding2010}
Spalding, M., Kainuma, M., Collins, L., 2010. World Atlas of Mangroves.
  Earthscan, London, UK and Washington DC, USA.

\bibitem[{Twilley et~al.(1992)Twilley, Chen, and T.}]{Twilley1992}
Twilley, R.~R., Chen, R., T., H., 1992. {Carbon sinks in mangroves and their
  implications to carbon budget of tropical coastal ecosystems}. Water, Air and
  Soil Pollution 64, 265--288.

\bibitem[{Wang et~al.(2013)Wang, Guan, Peart, Chen, and Peng}]{Wang2013539}
Wang, G., Guan, D., Peart, M., Chen, Y., Peng, Y., 2013. Ecosystem carbon
  stocks of mangrove forest in yingluo bay, guangdong province of south china.
  Forest Ecology and Management 310, 539 -- 546.
\newline\urlprefix\url{http://www.sciencedirect.com/science/article/pii/S0378112713005720}

\bibitem[{{World Bank}(2010)}]{WorldBank2010}
{World Bank}, 2010. {Capturing and conserving natural coastal carbon : building
  mitigation, advancing adaptation}. Tech. rep., World Bank; IUCN; ESA PWA.

\bibitem[{Yepes et~al.(2016)Yepes, Zapata, Bolivar, Monsalve, Milena,
  Sierra-correa, and Sierra}]{Yepes2016}
Yepes, A., Zapata, M., Bolivar, J., Monsalve, A., Milena, S., Sierra-correa,
  P.~C., Sierra, A., 2016. {Ecuaciones alom{\'{e}}tricas de biomasa a{\'{e}}rea
  para la estimaci{\'{o}}n de los contenidos de carbono en manglares del Caribe
  Colombiano} 64~(June), 913--926.

\end{thebibliography}

\clearpage

\section*{Figure captions}

\newpage

% Figure 1
\begin{figure}
%\includegraphics[%scale=0.4
%width=\textwidth
%]{Figures/Cdensity_and_TotalCstock.pdf} 
\caption{Aboveground biomass (AGB) density (Mg C ha$^{-1}$) and total carbon stock in AGB for Colombian mangroves (Tg C).} \label{fig:Csotck}
\end{figure}

% Fig 2
\begin{figure} 
%\includegraphics[%scale=0.4
%width=\textwidth
%]{Figures/AGBsamplingEffort.pdf} 
\caption{Number of necessary sampling units of AGB density required to reduce current uncertainties at 10\% and 5\% level for Caribbean, Pacific and total Colombian mangroves.} \label{fig:samplingEffort}
\end{figure}

% Figure 3
\begin{figure} 
%\includegraphics[%scale=0.4
%width=\textwidth
%]{Figures/Globalmodelsvs.pdf} 
\caption{ Observed vs. predicted AGB density (Mg ha$^{-1}$). Predicted values: using global models \citep{Twilley1992, CONL:CONL12060} and observed data: current data available for mangrove areas in Colombia} \label{fig:globalModels}
\end{figure}

% Fig 4
\begin{figure} 
%\includegraphics[%scale=0.4
%width=\textwidth
%]{Figures/AGBdensity_map_final.pdf} 
\caption{Map of predicted AGB density (Mg ha$^{-1}$) based on the candidate models classified as ``substantial weight models''} \label{fig:Predicted AGB density map}
\end{figure}
